CdGF_aucrf

### 2016-09-30 code/CdGF_AUCRF.Rmd
remove extra models from ROC plot

```{r}
pack_used <- c('randomForest','miscTools','ggplot2','reshape2', 'pROC', 'knitr', 'cowplot','dplyr','AUCRF')
for (dep in pack_used){
  if (dep %in% installed.packages()[,"Package"] == FALSE){
    install.packages(as.character(dep), repos = 'http://cran.us.r-project.org', 
                     quiet=TRUE);
  }
  library(dep, verbose=FALSE, character.only=TRUE)
}
```

@@

# create RF model
set.seed(seed)
rf_early_aucrf <- AUCRF(Euth_Early ~ ., data = Predict_early_euth_df,
                              ntree = n_trees, pdel = 0.05, ranking = 'MDA')
summary(rf_early_aucrf)
otu_euth_probs <- predict(rf_early_aucrf$RFopt, type = 'prob')
otu_euth_roc <- roc(Predict_early_euth_df$Euth_Early ~ otu_euth_probs[ , 2])
set.seed(seed)
random_roc <- roc(sample(c(1,0), length(otu_euth_probs[ , 2]), replace = T) ~ otu_euth_probs[ , 2])

@@

LOcO_probs <- c()
for(i in 1:length(cage_list)){
  by_cage <- LOcO_df$cage_id == cage_list[i]
  LOcO_predict <- select(LOcO_df, -cage_id)
  train <- LOcO_predict[!by_cage,]
  test <- LOcO_predict[by_cage,]
  set.seed(seed)
  temp_model <- AUCRF(Euth_Early~., data=train, pdel=0.99, ntree=500)
  LOcO_probs[LOcO_df$cage_id == cage_list[i]] <- predict(temp_model$RFopt, test, type='prob')[,2]
}
LOcO_roc <- roc(LOcO_df$Euth_Early~LOcO_probs)

LOcO_cv10f_aucs <- c()
LOcO_cv10f_all_resp <- c()
LOcO_cv10f_all_pred <- c()
for(j in 1:iters){
  set.seed(j)
  shuffle <- runif(nrow(LOcO_df))
  LOcO_df_r <- LOcO_df[order(shuffle), ]
#  sampling <- sample(1:nrow(LOcO_df),nrow(LOcO_df),replace=F)
  LOcO_cv10f_probs <- rep(NA,nrow(LOcO_df_r))
  for(i in 1:length(cage_list)){
    by_cage <- LOcO_df_r$cage_id == cage_list[i]
    LOcO_predict <- select(LOcO_df, -cage_id)
    train <- LOcO_predict[-by_cage,]
    test <- LOcO_predict[by_cage,]
    set.seed(seed)
    temp_model <- AUCRF(Euth_Early~., data=train, pdel=0.99, ntree=500)
    LOcO_cv10f_probs[by_cage] <- predict(temp_model$RFopt, test, type='prob')[,2]
  }
  LOcO_cv10f_roc <- roc(LOcO_df_r$Euth_Early~LOcO_cv10f_probs)
  LOcO_cv10f_all_pred <- c(LOcO_cv10f_all_pred, LOcO_cv10f_probs)
  LOcO_cv10f_all_resp <- c(LOcO_cv10f_all_resp, LOcO_df_r$Euth_Early)
  LOcO_cv10f_aucs[j] <- LOcO_cv10f_roc$auc
}
LOcO_cv10f_roc <- roc(LOcO_cv10f_all_resp~LOcO_cv10f_all_pred)

#### Random - 10-fold Cross validated - 10 repetitions

set.seed(seed)
ran_outcome_data <- cbind(Euth_Early = factor(sample(Predict_early_euth_df$Euth_Early,  
                                                     nrow(Predict_early_euth_df))), 
                             Predict_early_euth_df[,rf_early_aucrf$Xopt]) 
predict_random <-  predict(rf_early_aucrf$RFopt, ran_outcome_data, type = 'prob')[,2]
predict_random_roc <- roc(ran_outcome_data$Euth_Early ~ predict_random)

@@

@@

### Validate AUCRF with Randomized Input

```{r Random_validation, fig.width=6, fig.height=5, results= 'hide'}

# boruta feature selection
#set.seed(seed)
#Boruta(Euth_Early ~ ., data = Validate_early_euth_df, maxRuns = 200)
```

### Add ranges to RF ROC ??

```{r error_plot, eval=F}

caretmodel <- function(x) {
  fitControl <- trainControl(method = "repeatedcv",
    number = 10,
    repeats = 10,
    classProbs = TRUE,
    summaryFunction = twoClassSummary,
    savePredictions = TRUE)
  model <- train(Euth_Early ~ ., data=x, 
                 trControl=fitControl, method="rf", metric="ROC")
  return(model)
}
test <- aucrf_data
test$Euth_Early <- factor(ifelse(test[ , 'Euth_Early'] == 1, 'Late', 'Early'))
random <- test
set.seed(seed)
random$Euth_Early <- sample(random$Euth_Early, nrow(random))
caret_aucrf <- caretmodel(test)
caret_random <- caretmodel(random)
caret_prediction <- caretmodel(Predict_early_euth_df)

str(aucrf_data)
head(caret_aucrf$pred)

roclobster <- ggplot(caret_aucrf$pred, aes(d = obs, m = Late)) +
  geom_roc(n.cuts = 0) +
  theme_classic() +
  theme(
    axis.line.x = element_line(colour = "black"),
    axis.line.y = element_line(colour = "black")
  ) +
  geom_segment(aes(x = 0, y = 0, xend = 1, yend = 1), linetype=2) +
  ylab("Sensitivity") +
xlab(paste("Inverse Specificity"))

confusionMatrix(data = caret_aucrf$pred[,'pred'], reference = caret_aucrf$pred[,'obs'])
confusionMatrix(data = caret_random$pred[,'pred'], reference = caret_random$pred[,'obs'])

n <- nrow(Predict_early_euth_df)
indextrain <- sample(1:n,round(0.6*n),replace=FALSE)
Xtrain     <- Predict_early_euth_df[ indextrain,-1]
Xtest      <- Predict_early_euth_df[-indextrain,-1]
Ytrain     <- Predict_early_euth_df[ indextrain,1]
Ytest      <- Predict_early_euth_df[-indextrain,1]

qrf <- quantregForest(x=Xtrain, y=Ytrain, nodesize=10,sampsize=30)
conditionalQuantiles  <- predict(qrf, Xtest, what=sd)
print(conditionalQuantiles[1:4,])

### Other prediction models

##### C50

```{r c50, eval=F}
install.packages('C50')
library(C50)

set.seed(seed)
shuffle <- runif(nrow(Predict_early_euth_df))
Predict_early_euth_df_r <- Predict_early_euth_df[order(shuffle), ]

c50_euth_model <- C5.0(Predict_early_euth_df_r[1:50 , -1], Predict_early_euth_df_r[1:50 , 1])
summary(c50_euth_model)
plot(c50_euth_model)
c50_euth_predict <- predict(c50_euth_model, Predict_early_euth_df_r[51:55, ])
table(Predict_early_euth_df_r[51:55, 1],c50_euth_predict)

mylibrary<-c("SL.glm","SL.randomForest","SL.svm","SL.glmnet") 
SL_euth_model <- SuperLearner(as.numeric(Predict_early_euth_df_r[ , 1]), Predict_early_euth_df_r[ , -1], SL.library = mylibrary)
predict(SL_euth_model, newdata = as.numeric(Predict_early_euth_df_r[ , 1]))

SL_euth_model$SL.predict
sum=0
tt<-length(Predict_early_euth_df_r)
for(i in 1:tt) {
sum<-sum+(Predict_early_euth_df_r[i,1]-SL_euth_model$SL.predict[i])^2
  } 
sumg <-sum/tt
sumg

listWrappers()

Remove_otu_df <- Predict_early_euth_df_r %>% 
  select(-Otu00074, -Otu00114, -Otu00050, -Otu00124, -Otu00120, -Otu00100)

set.seed(seed)
rf_rm_otu_early_aucrf <- AUCRF(Euth_Early ~ ., data = Remove_otu_df,
                              ntree = n_trees, pdel = 0.05, ranking = 'MDA')
rm_otu_euth_probs <- predict(rf_rm_otu_early_aucrf$RFopt, type = 'prob')
rm_otu_euth_roc <- roc(Remove_otu_df$Euth_Early ~ rm_otu_euth_probs[ , 2])

plot(rm_otu_euth_roc, col='gray', lwd=2, add=T, lty=1)
```

>>>>

```{r}
pack_used <- c('randomForest','miscTools','ggplot2','reshape2', 'pROC', 'knitr', 'cowplot','dplyr','AUCRF','Boruta')
for (dep in pack_used){
  if (dep %in% installed.packages()[,"Package"] == FALSE){
    install.packages(as.character(dep), repos = 'http://cran.us.r-project.org', 
                     quiet=TRUE);
  }
  library(dep, verbose=FALSE, character.only=TRUE)
}
```

@@

# create RF model
set.seed(seed)
rf_early_aucrf <- AUCRF(Euth_Early ~ ., data = Predict_early_euth_df,
                              ntree = n_trees, pdel = 0.05, ranking = 'MDA')

otu_euth_probs <- predict(rf_early_aucrf$RFopt, type = 'prob')
otu_euth_roc <- roc(Predict_early_euth_df$Euth_Early ~ otu_euth_probs[ , 2])

@@

LOcO_probs <- c()
for(i in 1:length(cage_list)){
  by_cage <- LOcO_df$cage_id == cage_list[i]
  LOcO_predict <- select(LOcO_df, -cage_id)
  train <- LOcO_predict[!by_cage,]
  test <- LOcO_predict[by_cage,]
  set.seed(j)
  temp_model <- AUCRF(Euth_Early~., data=train, pdel=0.99, ntree=500)
  LOcO_probs[LOcO_df$cage_id == cage_list[i]] <- predict(temp_model$RFopt, test, type='prob')[,2]
}
LOcO_roc <- roc(LOcO_df$Euth_Early~LOcO_probs)

@@

Leave 1 cage out RF with all otus gives and AUC of 0.63-0.68, but using the reduced features selected by AUCRF on the whole dataset gives an AUC of 0.88-0.90

@@
